% recipient data
\recipient{}

% Company Recruitment team}{Company, Inc.\\123 somestreet\\some city

\date{\today}
%\subject{Job application}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
\enclosure[Attached]{Curriculum Vitae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname

\makelettertitle

 My recent academic journey culminated in the study of an MSc in Applied Data Science, wherein I acquired an understanding of complex machine learning models, bias mitigation, data analysis, networking and electrical engineering gaining professions in programming languages such as python and R.  During this course, I studied Big Data gaining skills with technologies such as Apache Spark and Kubernettes.
 
 Having successfully earned a BSc in Web Technologies and Digital Media in 2021, I gained hands-on experience in crafting digital products ranging from websites to interactive video content, employing principles of User-Centred Design and Agile methodologies. Therefore, I can work with modern front-end workflows using javascript frameworks like node and react. Furthermore, during the course I used various programming languages such PHP, C# and Python. 
 
 
 I am proficient with PHP frameworks such as Laravel and Magento, including WordPress, during my course a Wordpress plugin was developed that transformed a website into a single-page application, alongside developing an administration module to fine-tune its functionality. 
I am familiar with Excel, using it to provide descriptive statistics and graphs for customer surveys and break-even analysis. 
 
 to other frameworks  

 
 unit testing techniques, including unit testing, acceptability, and integration testing. In addition, I can follow clean coding principles such as SOLID.
 
In addition, I am interested in knowledge discovery in databases and business process mining, having researched the topics during my bachelor's dissertation. , 







Furthermore,


I developed a using e. 
the work experience module, 




in plugin development during my 


\makeletterclosing