
\cventry{2017--2019}{Blackpool}{Tower Employment Services}{Catering Team Member}
\newline{}As a dedicated catering team member, I excelled in diverse roles across the Fylde Coast, participating in events such as the Blackpool Lights Switch On and Rebellion at Winter Gardens. I adeptly handled cash transactions, integrated seamlessly into collaborative teams, and thrived in fast-paced, high-energy settings.  I also maintained high service and standards at various locations, including Ribby Hall's The Bar and Grill and the Tapas Bar and Banqueting. 


\cventry{2010--2012}{Blackpool}{New President Hotel}{Kitchen Assistant}{}{
I worked as a kitchen assistant I set up the breakfast bar in the mornings and also served food as a waiter in the evenings. 
}
\vspace{1cm}
\cventry{2010--2012}{Blackpool}{Dahlias Kitchen}{Bar}{}{
I worked at the bar at the garden centre over weekends, and I helped on busy theme nights, helping on the bar, serving food and cleaning up afterwards.
}

\vspace{1cm}
\cventry{July 2010- December 2010}{Blackpool}{Imperial Hotel}{Waiter}{}{
\newline{}
I worked as a waiter taking on bar duties and silver service. I used effective communication skills delivering excellent customer service. I actively participate in staff training sessions to foster a culture of excellence.
}
\vspace{1cm}
\cventry{2008--2010}{Blackpool}{The Garden Place}{General Assistant}{}{
I assisted customers in finding plants, gardening supplies and I demonstrated an in-depth knowledge of various plant species, their care requirements, and landscaping techniques, allowing me to offer informed recommendations and advice to customers. I played a role in inventory management, including restocking shelves, organizing merchandise, and creating visually appealing displays and product placements throughout the store. 
}


\cventry{June 2007-- September 2007}{Waiter}{Lancastrian Chip Shop}{Blackpool}{}{
\newline{}
I worked as a waiter in a cafe and also the fish shop.
}






